The \proglang{R} Package \pkg{forestinventory}: Design-Based Global and Small Area Estimations for Multiphase Forest Inventories

### 2017-08-31 JStatSoft_forestinventory_master.rnw
Changes to abstract to make more concise.

%% an abstract and keywords
\Abstract{
Forest inventories provide reliable and evidence-based information to assess the state and development of forests over time. The information is collected at discrete sample locations distributed over the forest area by means of statistical sampling methods. This sample is then used to provide estimates of a target variable for a given spatial unit. Due to the high costs of the terrestrial campaigns, there is a need for alternative methods that can provide a) the same estimation precision at lower costs or b) higher estimation precision at identical costs. With respect to this objective, the application of double and triple-sampling regression estimators (so-called \textit{multi-phase} forest inventory methods) has proved to be efficient. The core concept of multi-phase methods is to combine the terrestrial sample with a much larger sample of target variable \textit{predictions} based on \textit{auxiliary information} that is available in high quantity and low costs. Whereas these methods have been successfully applied in practice, the availability of repective open-source software has been rare up to non-existent. The \proglang{R} package \pkg{forestinventory} provides a comprehensive set of global and small area regression estimators for multi-phase forest inventories under simple and cluster sampling. The implemented methods have been demonstrated in various scientific studies covering small to large scale forest inventories, and can be used for double and triple sampling for stratification, regression and regression within strata. This article provides a bridge from a mathematical summary of the estimators to their implementation and application in \proglang{R}.}

\Keywords{forest inventory, design-based, infinite population approach, two and three-phase sampling, regression estimators, small area estimation}
\Plainkeywords{forest inventory, design-based, infinite population approach, two and three-phase sampling, regression estimators, small area estimation}

>>>>

%% an abstract and keywords
\Abstract{
Forest inventories provide reliable and evidence-based information to assess the state and development of forests over time.  They typically consist of a random sample of plot locations in the forest that are assessed individually by hand. Due to the high costs of these terrestrial campaigns, remote sensing information available in high quantity and low costs (e.g. LiDAR, stereophotogrammetry, etc.) is frequently incorporated in the estimation process in order to reduce inventory costs or improve estimation precision. With respect to this objective, the application of \textit{multiphase} forest inventory methods (e.g. double- and triple-sampling regression estimators) has proved to be efficient. While these methods have been successfully applied in practice, the availability of open-source software has been rare if not non-existent. The \proglang{R} package \pkg{forestinventory} provides a comprehensive set of global and small area regression estimators for multiphase forest inventories under simple and cluster sampling. The implemented methods have been demonstrated in various scientific studies ranging from small to large scale forest inventories, and can be used for post-stratification, regression and regression within strata. This article summarizes the mathematical theory of this family of design-based estimators and demostrates how they can be easily implemented in \proglang{R}.}

\Keywords{forest inventory, design-based, infinite population approach, two- and three-phase sampling, regression estimators, small area estimation}
\Plainkeywords{forest inventory, design-based, infinite population approach, two- and three-phase sampling, regression estimators, small area estimation}
